\documentclass[a4paper,12pt]{cv4tw}
\usetheme[minuit]{sharp}

\firstname{Alex}
\lastname{O'Brien}

\setcvcontact[email]{alex@emobrien.com}
\setcvcontact[cellphone]{0421914822}
\setcvcontact[github]{3541}
\setcvcontact[spokenlanguages]{en, es}

\title{}
\begin{document}
\section{Education}
\story{Math Extension}{Monash University}{2019}{}{}
\story{VCE}{John Monash Science School}{2017--2019}{}{
    Relevant achievements and experience:
    \begin{missions}
    \item \href{https://beamlineforschools.cern/}{CERN Beamline for Schools competition} -- \textit{\href{https://beamline-for-schools.web.cern.ch/sites/beamline-for-schools.web.cern.ch/files/BL4S_shortlisted_teams_2019.pdf}{Shortlisted}, see projects}
    \item Debaters Association of Victoria -- \textit{Swannie Award}
    \item Algorithmics (HESS) -- \textit{43 study score (35 raw)}
    \item Physics Olympiad -- \textit{High Distinction}
    \end{missions}
}
\story{AP}{University Prep}{2016--2017}{}{
    Subjects:
    \begin{missions}
    \item Calculus AB
    \item Computer Science
    \end{missions}
}
\section{Experience}
\story{Catering}{Royal Brighton Yacht Club}{2019}{Catering\\Customer Service}{Worked over the summer and during the school year on a casual basis, developing useful experience in customer service and relations.}
\story{IT}{University Prep}{2016--2017}{IT\\Support\\Systems Administration}{
    Worked two summers in general IT and support, involving a variety of tasks in multiple areas of expertise. Some relevant functions performed include:
    \begin{missions}
    \item Image creation for the upgrade to Windows 10 -- involved the following tasks:
        \begin{itemize}
            \item Extensive driver testing and management for every device in the organization.
            \item Upgrade and maintenance of the FOG driver installation script to offload to the Windows 10 automatic driver installation, reducing error and ensuring drivers installed were up-to-date.
        \end{itemize}
    \item Maintenance of the FOG imaging system, including the setup for multiple new device models.
    \item Maintenance of the Casper Suite imaging system, including the deployment of a new system image.
    \item Major software upgrade for the Casper/OpenDirectory/ProfileManager server.
    \item Deployment and management for a thin client system for the school library checkout using Raspberry Pis.
    \item Management, imaging, and upgrades for a digital signage system on Mac Minis.
    \item Device setup for new staff and equipment -- imaging, testing, etc.
    \item Miscellaneous diagnostic tasks and technical support for staff.
    \end{missions}
    Relevant technologies used include:
    \begin{missions}
    \item Microsoft Active Directory
    \item Apple Open Directory and Profile Manager
    \item FOG Imaging
    \item Casper Suite (now jamf PRO)
    \item Raspberry Pi
    \end{missions}
}
\section{Skills}
\begin{skills}{Computing}
    \skill[Fundamentals]{Solid understanding of fundamental operations of computer hardware and software, including CPU architecture and components.}
    \skill[Programming]{Knowledge of a wide variety of languages and paradigms, including object-oriented and functional practices. Primarily experienced in Rust and C/C\ensuremath{+}\ensuremath{+}, with working knowledge of Python, Java, Go, and others.}
    \skill[Systems]{Long-time interest in systems programming. Knowledge of operating systems design and implementation, as well as compilers. Competent in x86\_64 assembly.}
    \skill[Security]{Understanding of security best-practices and fundamentals. Able to securely administer common Linux services such as nginx and Apache. Experience in the theory of software exploitation and reverse engineering, including binary reverse engineering with the Ghidra software.}
    \skill[Operations]{Experience both in a personal and professional context with the administration of common enterprise technologies, including: \begin{itemize}
            \item Windows -- Administration and management, including Active Directory
            \item macOS -- Administration and management, including Active Directory and Profile Manager
            \item Linux -- Administration and management of servers, workstations, and thin/embedded devices
            \item Other *nix -- Working familiarity with BSDs (FreeBSD and OpenBSD in particular)
            \item FOG Imaging -- Management, maintenance, and internals, as well as use of Windows tools such as sysprep in this context
            \item nginx -- Operation and maintenance, security and crypto best practices
            \item Apache -- (As above)
        \end{itemize}
    }
\end{skills}
\begin{skills}{Communication}
    \skill[Written]{Strong written communication skills both in an informative and argumentative style}
    \skill[Spoken]{Experience in competitive speaking and debate}
    \skill[Instruction]{Served as a mentor in mathematics for younger students}
\end{skills}
\begin{skills}{Other Interests}
    \skill[Machine Learning]{A basic familiarity with theory and practice}
    \skill[Compilers]{Fascination with the subject, currently working on a rudimentary C compiler}
    \skill[Physics]{Deep interest in the field, particularly in particle physics, astrophysics, and cosmology}
\end{skills}
\section{Projects}
Names are hyperlinked.
\story{\href{https://github.com/3541/3cc}{3cc}}{C Compiler}{2019}{Compilers\\Parsing}{A basic C compiler in Rust. Currently implements most basic operators, but does not understand variables.}
\story{\href{https://beamlineforschools.cern/editions/2019-edition}{Beamline for Schools}}{Physics Competition}{2019}{Particle Physics\\Written Communication}{A competition organized by CERN in which secondary school teams submit proposals for an experiment to be conducted using a particle accelerator. Project, involving screening various types of non-volatile memory technology for radiation resistance, was \href{https://beamline-for-schools.web.cern.ch/sites/beamline-for-schools.web.cern.ch/files/BL4S_shortlisted_teams_2019.pdf}{shortlisted}.}
\story{\href{https://github.com/3541/syzygy}{Syzygy}}{Kernel}{2018--2019}{Operating Systems\\Computer Architecture}{A rudimentary, work-in-progress kernel implemented in Rust.}
\story{\href{https://github.com/3541/handwriting_recognition_example}{Handwriting Recognition}}{Neural Network}{2018}{Machine Learning\\Neural Netowrks}{A sample neural network trained to recognize handwritten characters, done for a Wolfram class in 2018.}
\end{document}
